Sound Synthesis

### 2020-11-04 Text/04_Theory.tex
some progress

To keep our roots in the physical case, we`ll also assume that a wave with a zero phase has an instantaneous amplitude of zero at time zero, as is the case of the sine wave, for example.

@@

First, it is necessary to stablish a correspondence between a continuous and a discrete wave, as the latter will be the object of most of this work. To do that we will define a simple continuous sinusoidal wave of the form $ S(t) = a \cos \left( \phi + 2 \pi \mathcal{F} t \right) $, where $ a \in \mathbb{R}^+ $ is the amplitude; $ \phi \in \mathbb{R}^+, 0 \le \phi < 2 \pi $ is the phase; $ \mathcal{F} \in \mathbb{R}^+ $ is the absolute frequency of the wave, in Hz and $ t \in \mathbb{R} $ is time, in seconds.

The cosine function is used for a twofold reason: it is historical background, and its use helps to underline the periodic nature of the wave in consideration. It is important to keep in mind, however, that this discussion applyes any arbitrary function of the form $ f(x) = f(x + P) \forall x \in D(f) $, where $ D $ is the domain of the function $ f $.
% TODO This will be further illustrated in the discrete part below.

>>>>

We are going to also assume that a wave with a zero phase has an maximum instantaneous amplitude at time zero, as is the case of the cosine wave, for example. Altough that assumption somewhat departs from the physical intuition, it is useful in making our description consistent with the theory behind the Fourier Transform.

@@

First, it is necessary to establish a correspondence between a continuous and a discrete wave, as the latter will be the object of most of this work. To do that we will define a simple continuous sinusoidal wave of the form $ S(t) = a \cos \left( \phi + 2 \pi \mathcal{F} t \right) $, where $ a \in \mathbb{R}^+ $ is the amplitude; $ \phi \in \mathbb{R}^+, 0 \le \phi < 2 \pi $ is the phase; $ \mathcal{F} \in \mathbb{R}^+ $ is the absolute frequency of the wave, in Hz and $ t \in \mathbb{R} $ is time, in seconds.

The cosine function is used for a twofold reason: its use helps to underline the periodic nature of the wave in consideration and is the parameter of the phase when the FT is used. It is important to keep in mind, however, that this discussion applies any arbitrary function of the form $ f(x) = f(x + P) \forall x \in D(f) $, where $ D $ is the domain of the function $ f $.
% TODO This will be further illustrated in the discrete part below.
